---
title: "FMM"
author: "Megan Sporre"
date: "March 5, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
paternal<-read.csv("../Data/kichler_paternal.csv")
paternal[is.na(paternal)]=0 #change any columns with no value (NA) to 0
MP<-apply(paternal[,grep("pat", names(paternal))],1,function(x) 1*any(x>2)) #list of broods with more than 2 paternal alleles at any given locus
MP
Mult.Pat<-as.data.frame(cbind.data.frame(paternal$Brood_ID, MP))#create data frame of all broods
colnames(Mult.Pat)<- c("Brood_ID", "MP") #rename columns of data frame



Pm<- sum(Mult.Pat$MP)/length(Mult.Pat$MP)
Pm #proportion of broods with multiple paternity

#calculate
max_palleles<-apply(paternal[,grep("pat_",names(paternal))],1,FUN=max)
min_sires<-max_palleles/2
F<-as.data.frame(cbind.data.frame(paternal$Brood_ID, ceiling(min_sires)))
colnames(F)<- c("Brood_ID", "F") #may need just single column
F




#DETERMINE ALLELE FREQUENICUES FOR ALL LOCI FROM MATERNAL AND OFFSPRING ALLELES
maternal<-read.csv("../Data/kichler_maternal.csv",as.is=T)
maternal
offspring<-read.csv("../Data/kichler_offspring.csv",as.is=T)
offspring

rawalleles<-rbind(maternal,offspring[,-3])
nloc=((dim(rawalleles)[2]-2)/2)
lst=vector("list",nloc)
for (i in 0:(nloc-1))
{
  print(2+((2*i)+1):((2*i)+2)) #printing the column numbers that function is using
temp=rawalleles[,2+((2*i)+1):((2*i)+2)]
tb1<-unlist(temp)
tb1=tb1[tb1!=""]
tbl<-table(tb1)
tbl=tbl[tbl>0]
lst[[i+1]]=data.frame(frq=tbl/sum(tbl))
}
lst


mgenos<-maternal[,-c(1:2)]


```
```{r}

sk<-read.csv("../Data/skew.csv")
sk

freqs = list(data.frame(frq=rep(0.1,10)),
                    data.frame(frq=rep(0.1,10)),
                    data.frame(frq=rep(0.2,5)))
freqs
lst
```

```{r}
af=lst

# for each of B broods, generate genotypes for F sires based on population allele frequencies
sires<- with(F, rep(Brood_ID, times = F))
sire_genotypes<-data.frame(sires)
sire_genotypes[,colnames(maternal[,-c(1:2)])]=NA
for (i in 0:(nloc-1))
  sire_genotypes[,1+((2*i)+1):((2*i)+2)]=sample(af[[i+1]][,1],2*length(sires),prob =af[[i+1]][,2],replace=T )
sire_genotypes


```
```{r}
Cb<-data.frame(table(offspring$Brood_ID))
names(Cb)=c("Brood_ID","Cb")
Cb
```
```{r}
pseudo_broods=NULL
for (b in Cb$Brood_ID)
{
  sires1=sire_genotypes[sire_genotypes$sires==b,]
  rn=dim(sires1)[1]
  
  maternal1=maternal[maternal$Brood_ID==b,]
  #print(Cb$Cb[Cb$Brood_ID==b])
    for (r in 1:Cb$Cb[Cb$Brood_ID==b])
  {
    
       if (rn>1)
    {sirerow=sample(1:dim(sires1)[1],1,prob = sk[,1])} else 
    {sirerow=1}
      pseudo_ogeno<-rep(-1,dim(maternal1)[2]-2)
      for (i in 0:(nloc-1))
      {
        mloc=maternal1[,2+(2*i+1):(2*i+2)]
        ploc=sires1[sirerow,1+(2*i+1):(2*i+2)]
        mallele=unlist(sample(mloc,1))
        pallele=unlist(sample(ploc,1))
        oloc=as.numeric(c(mallele,pallele))
        pseudo_ogeno[(2*i+1):(2*i+2)]=oloc
      }
      pseudo_broods=rbind(pseudo_broods,
                          data.frame(Brood_ID=b,matrix(pseudo_ogeno,nrow=1)))
  #print(b)
     #print(r) 
  #print(sires1[sirerow,"sires"])
  }
}


```

```{r}
#determine Pm and Pr(Pm|fmm)
library(dplyr)
allele_counts<-pseudo_broods%>%group_by(Brood_ID)%>%summarise_all(.funs=function(x){length(unique(x))})

palleles<-allele_counts[,as.logical((1:dim(allele_counts)[2])%%2)]#create vector for number of paternal alleles at each locus for each brood
palleles

MP_pseudo<-apply(palleles[,-1],1,function(x) as.numeric(sum(x>2)>0))

apply(palleles[, seq(2,ncol(pseudo_broods),2)],2,function(x) 1*x>2) #list of broods with more than 2 paternal alleles at any given locus



Pm_pseudo<- sum(MP_pseudo)/length(MP_pseudo)
Pm_pseudo #proportion of broods with multiple paternity
```


```{r}
onelocpseudo=function(F,af) #generate male genotypes based on known allele frequencies
  {genos=data.frame(a1=rep(-1,F),a2=rep(-1,F))
  for(i in 1:F)
      {genos[i,1]=sample(1:dim(af)[1],1,prob=af[,1])
        genos[i,2]=sample(1:dim(af)[1],1,prob=af[,1])
      }
      genos}


pseudobrood<-function(F,freqs) #create a ragged list object (freqs) where each element is a 1-column df with rows representing alleles and elements in the column representing frequencies
{
  lst<-lapply(freqs,function(f)
   {
    onelocpseudo(F,f)
    })
  allgenos=do.call(cbind,lst)
  allgenos
}


choose_sire<-function(sk,genos) #for each offspring within a pseudobrood, probabalistically select a sire based on mean paternal skew (may be able to simulate skew later on)
{
  genos[sample(1:dim(genos)[1],1,prob=sk[,1]),]
}

reproduce<-function(mgeno,F,sk,freqs) #randomly assign one allele from each mother and selected father to at each loci for each brood
{
  ogeno<-rep(-1,length(mgeno))
  fgenos<-pseudobrood(F,freqs)
  print("tish far")
  fgeno<-choose_sire(sk,fgenos)
  numloc=length(mgeno)/2
  for(i in 0:(numloc-1))
  {
    mloc=mgeno[(2*i+1):(2*i+2)]#choose one allele from col 1+2 and 3+4, etc
    floc=fgeno[(2*i+1):(2*i+2)]#choose one allele from col 1+2 and 3+4, etc
    mallele=sample(mloc,1)
    fallele=sample(floc,1)
    oloc=c(mallele,fallele)
    ogeno[(2*i+1):(2*i+2)]=oloc
  }
  ogeno
}
reproduce(mgenos,F,sk,freqs)

```

```{r}


```

MP<-apply(genetics[,grep("Paternal", names(genetics))],1,function(x) 1*any(x>2)) #list of broods with more than 2 paternal alleles at any given locus
Mult.Pat<-as.data.frame(cbind(genetics$Nest_.,MP)) #create data frame of all broods
colnames(Mult.Pat)<- c("Brood #", "Detection of Multiple paternity") #rename columns of data frame
Mult.Pat


Pm<- sum(Mult.Pat$`Detection of Multiple paternity`)/length(Mult.Pat$`Detection of Multiple paternity`)
Pm #proportion of broods with multiple paternity

#calculate minimum number of sires for each brood
max_pat_alleles<-apply(genetics[,grep("Paternal",names(genetics))],1,FUN=max)
max_pat_alleles
min_sires<-max_pat_alleles/2
F<-as.data.frame(cbind(genetics$Nest_.,ceiling(min_sires)))
colnames(F)<- c("Brood", "Minimum.Number.of.Sires") #may need just single column
F